---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error =T)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1603779702200-95b2785f2083?q=80&w=1587&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Making pies with ggplot2]
## .small[featuring `coord_polar(theta = "y")`, `geom_bar(position = "fill")`, `stage()`, and {ggtrace}]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: 
Nathan Dumlao, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)

diamonds %>%
ggplot() + 
  aes(x = 0) + 
  geom_bar(position = "fill") + 
  aes(fill = cut) +
  stat_count(
    geom = "text", position = "fill", 
    color = "white", size = 8,
    aes(x = .25,
        label = after_stat(
          count*100/sum(count)) |> 
          round(1) |> 
          paste0("%"))) +  
  # usually would include this in above function
  aes(y = stage(start = NULL, 
                  after_stat = count,
                  after_scale = (ymin + 
                                   ymax)/2)) +
  coord_polar(theta = "y") + 
  theme_void() ->
classic_pie
```


---

# ggtrace may help clarify strategy? 

```{r}
ggtrace::layer_before_stat(classic_pie, i = 2)
```


---

# ggtrace may help clarify strategy? 

```{r}
ggtrace::layer_after_stat(classic_pie,i = 2)
```


---

# ggtrace may help clarify strategy? 

```{r}
ggtrace::layer_after_scale(classic_pie, i = 2) %>% data.frame()
```



---

### Learn more:

- https://yjunechoe.github.io/ggtrace/


---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette



