---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error =T)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1603779702200-95b2785f2083?q=80&w=1587&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Making pies in ggplot2]
## .small[featuring `coord_polar(theta = "y")` and `geom_bar(position = "fill")`]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: 
Nathan Dumlao, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)

diamonds %>%
ggplot() + 
  aes(x = 0) + 
  geom_bar(position = "fill") + 
  aes(fill = cut) +
  coord_polar(theta = "y") + 
  theme_void() + 
  stat_count(position = "fill", 
             geom = "text", 
             color = "white",
             size = 8,
             aes(label = 
                   after_stat(count*100/sum(count)) |> 
                      round(1) |>   
                      paste0("%"))) ->
  classic_pie
```

---

# First attempt at moving labels to wedge centers *fails*

```{r, error = T}
classic_pie + 
    stat_count(position = "fill", 
             geom = "text", 
             color = "white",
             size = 8,
             aes(label = 
                   after_stat(count*100/
                                sum(count)) |> 
                   round(1) |> paste0("%"),
                 y = after_scale((ymin + 
                                    ymax)/2)))
```


---

# can ggtrace help? 

```{r}
ggtrace::layer_after_stat(classic_pie,i = 2, verbose = T)
ggtrace::layer_after_scale(classic_pie, i = 2, verbose = T) %>% data.frame()
```



---
class: inverse, center, middle

# And a little ggpie preview... 

```{r}
Titanic %>% 
  data.frame() %>% 
  uncount(Freq) ->
tidytitanic

```

---


`r flipbookr::chunk_reveal("feature2", widths = c(1,1))`


```{r feature2, echo = F, out.width="70%", fig.align='center', include = F}
library(ggpie)
tidytitanic %>%
  ggpie() + 
   geom_wedge() + 
   aes(fill = Sex) + 
  facet_wrap(~Sex) + 
  aes(fill = Class) + 
  facet_grid(Sex ~ Class) + 
  aes(fill = Survived)
```


---

### Contribute

- https://github.com/EvaMaeRey/ggpie (may become ggwedge)


---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette



