---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1606482659485-8b5c3623a609?q=80&w=1473&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# An advent of code calendar]
## .small[featuring experimental [{ggcalendar}](https://github.com/EvaMaeRey/ggcalendar)]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Elena Mozhvilo, Upsplash]
???
Title 

---

## Build dates data frame

```{r}
library(tidyverse)
"2023-12-01" %>% 
  as_date() +
  days(0:30) ->
december_vec

c(NA, NA, NA, "make calendar", "make 9 pies", "circle pack counting",
  "pivot w OOP", "RUGS check", "smoothfit", "slice", "nc w sf", "org extenders", "sample") %>% 
  c(., rep(NA,31-length(.))) %>% 
  tibble(todo = .) %>% 
  mutate(date = december_vec) ->
advent_df

```


---

`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(ggcalendar)

advent_df %>% 
  ggcalendar(dates_df = .) + 
  aes(date = date) + 
  geom_tile_calendar(color = "oldlace", 
                     linewidth = .5,
                     fill = "darkolivegreen") + 
  aes(alpha = date < Sys.Date()) +
  geom_text_calendar(alpha = .4) + 
  aes(color = date < Sys.Date()) + 
  scale_color_manual(values = c("grey30", "grey95"),
                     label = c("future", "past")) +
  scale_alpha_discrete(label = c("future", "past")) +
  geom_text_calendar(
    aes(label = str_wrap(todo, 7)),
    lineheight = .7,
    alpha = .8) + 
  theme(text = element_text(size = 20)) + 
  labs(alpha = NULL, color = NULL) + 
  labs(title = "'Advent of Code'") +
  geom_tile_calendar(data = . %>% 
                       filter(date == Sys.Date()),
                     fill = alpha("goldenrod2", .1),
                     color = "goldenrod3", 
                     show.legend = F,
                     linewidth = 1.5)
```



---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 



---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

