---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, cache = T)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{}]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Denise Jans, Upsplash]
???
Title 

---


```{r}
library(tidyverse)
library(ggcirclepack)

# tidytuesday data
rladies_chapters_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-21/rladies_chapters.csv') %>% 
  mutate(chapter = str_remove(chapter, "rladies-") %>% 
           str_replace_all("-", " ") %>% str_to_title() %>% str_remove("\\s+$")) 
```


---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
rladies_chapters_raw %>% 
  group_by(chapter) %>% 
  summarise(first_date = as.Date(min(date)),
            last_date = as.Date(max(date)),
            tot_meetings = n()) %>% 
  arrange(first_date) %>% 
  mutate(chapter = fct_inorder(chapter)) ->
rladies_chapter_df

rladies_chapters_raw %>% 
  mutate(chapter = 
           factor(chapter,
                     levels = 
                    levels(rladies_chapter_df$chapter))) %>% 
  group_by(chapter) %>% 
  mutate(meeting_number = rank(date)) ->
meetings_df

make_ordinal <- function(x){

  ifelse(x == 1, "1st",
         ifelse(x == 2, "2nd",
                ifelse(x == 3, "3rd", paste0(x,"th"))))

}
 
# test
make_ordinal(x = 1:10)
```


---


`r flipbookr::chunk_reveal("feature2", widths = c(1,1))`

---

```{r feature2, echo = F, fig.width=20, fig.height = 12}
meetings_df %>% 
  ggplot() + 
  aes(y = as.numeric(chapter), x = date) + 
  geom_point(alpha = .6) + 
  aes(color = meeting_number) +
  geom_text(data = rladies_chapter_df,
            aes(x = first_date-days(120), 
                label = ifelse(chapter == "San Francisco", 
                               "San         \nFrancisco",
                               as.character(chapter))),
            color = "grey20",
            hjust = 1,
            size = 4.5, 
            lineheight = .7) +
  geom_text(data = rladies_chapter_df,
            aes(x = last_date, 
                label = make_ordinal(tot_meetings)),
            color = "grey20",
            hjust = -.3,
            size = 4.5) +
  theme(axis.text.y = element_blank()) + 
  scale_color_viridis_c(option = "magma", breaks = c(1, 50, 100), 
                        labels = c("1st", "50th", "100th")) + 
  facet_wrap( ~ cut_interval(
    as.numeric(chapter), 
    n = 4), 
    scales = "free_y", 
    ncol = 4) + 
  labs(color = "Meeting\nnumber") + 
  scale_x_date(expand = expansion(c(.3,.2)))
```


```{r}
rladies_chapters_raw %>% 
  ggplot() + 
  aes(date) + 
  geom_histogram(color = "white",
                 fill = "plum4",
                 linewidth = .2) +
  aes(alpha = location) + 
  scale_alpha_discrete(range = c(.9, .7)) + 
  theme_minimal() + 
  geom_vline(xintercept = as_date("2022-11-30"),
             linetype = "dashed",
             color = "grey40") + 
  geom_vline(xintercept = as_date("2013-12-25" ) + 
               years(0:10),
             color = "magenta",
             linetype = "dashed",
             alpha = .2) +
  geom_rug(alpha = .2,
           color = "plum4") + 
  labs(title = "") +
    ggstamp::stamp_curve(x = as_date("2024-09-25" ), y = 320,
                       xend = as_date("2022-11-30") + days(45), 
                       yend = 260, size = .5, 
                       curvature = -.2
                        ) +
  ggstamp::stamp_label(x = as_date("2025-09-25" ), y = 320,
                       label = "ChatGPT is\nreleased",
                       hjust = 1,
                       size = 4) 
```

```{r}
rladies_chapters_raw %>% 
  filter(year(date) == 2022) %>% 
  count(date) %>% 
  ggcalendar::ggcalendar() + 
  ggcalendar::geom_tile_calendar(data = ggcalendar::return_dates_year(2022), 
                                 aes(fill = NULL)) +
  ggcalendar::geom_tile_calendar() + 
  ggcalendar::geom_text_calendar() +
  aes(fill = n) + 
  scale_fill_viridis_c(limits = c(0,10))


rladies_chapters_raw %>% 
  ggplot() + 
  aes(x = "all", y = "all") +
  stat_sum(geom = "tile", alpha = .85) + 
  aes(fill = after_stat(n)) + 
  scale_fill_viridis_c(option = "magma", end = .9) +
  stat_sum(geom = "text",
           aes(label = after_stat(n)),
           color = "oldlace", 
           size = 3) +
  aes(y = year(date)) + 
  aes(y = year(date) |> as.character()) + 
  aes(x = month(date, label = T)) +
  aes(y = "all") +
  aes(x = as.factor(day(date))) + 
  aes(y = month(date, label = T)) + 
  aes(y = month(date, label = T) |> fct_rev())


ggwipe::last_plot_wipe_last() +
  facet_wrap(~year(date)) + 
  scale_x_discrete(breaks = as.character(1:31),
                   labels = c("1", rep("", 8), 
                              "10", rep("", 9),
                              "20", rep("", 10), "31"))
  
  
  
```


---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

