---
title: "#'Global Human Day' featurette"
subtitle: "featuring [{ggcirclepack}](https://github.com/EvaMaeRey/ggcirclepack) which is experimental"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
# remotes::install_github("EvaMaeRey/ggcirclepack")
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1504196606672-aef5c9cefc92?auto=format&fit=crop&q=60&w=500&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxzZWFyY2h8MTZ8fGJhbGxvb25zfGVufDB8fDB8fHww)
background-size: cover
# .Large[#'Global Human Day' featurette]
## .small[featuring [{ggcirclepack}](https://github.com/EvaMaeRey/ggcirclepack) which is experimental]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Gaelle Marcel, Upsplash]
???
Title 

---


```{r}
# tidytuesday data
tt_url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-31/horror_articles.csv" 
library(tidyverse)
library(ggcirclepack)

read_csv(tt_url) %>% 
  count(rating) ->
article_rating_count

```


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
article_rating_count %>% 
  ggplot() + 
  aes(id = as_factor(rating) %>% paste0("'", . ,"'")) + 
  geom_circlepack() + 
  coord_equal() +
  aes(fill = n) + 
  geom_circlepack_text(color = "white") + 
  aes(area = n) + 
  scale_fill_viridis_c(end = .7, option = "inferno") +
  scale_size_continuous(range = c(2, 6)) + 
  ggstamp::theme_void_fill(fill = "darkred") +
  theme(legend.position = "none") +
  labs(title = "Snopes investigation outcomes on 'horror articles'") + 
  theme(text = element_text(size = 15)) + 
  ggstamp::stamp_wash(alpha = .2, fill = "darkred")
```


---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion:  https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette

