---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring Hadley's waterfall chart from https://vita.had.co.nz/papers/ggplot2-wires.pdf]
#### .tiny[Gina Reynolds | 2024-01-03 |Image credit: Denise Jans, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---


```{r feature, include=F}
library(tidyverse)
data.frame(event = c("Starting Cash", 
                     "Sales", 
                     "Refunds",
                     "Payouts", 
                     "Court Losses", 
                     "Court Wins", 
                     "Contracts", 
                     "End Cash"),
           change = c(2000, 3400, -1100, 
                      -100, -6600, 3800, 
                      1400, -2800)) %>% 
  mutate(balance = cumsum(c(0, 
                            change[-nrow(.)]))) %>% 
  mutate(time = row_number()) %>% 
  mutate(flow = factor(sign(change))) ->
balance

ggplot(balance) +
          geom_rect(
            aes(xmin = time - 0.45, 
                xmax = time + 0.45, 
                ymin = balance, 
                ymax = balance + change)) +
          geom_text(aes(x = time, 
                        y = pmin(balance, 
                                 balance + change) - 50, 
                        label = balance))
```


---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

