---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: left
background-image: url(https://images.unsplash.com/photo-1533930086187-0fc58e5a92e2?q=80&w=1587&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# Prediction with [{ggsmoothfit}](https://github.com/EvaMaeRey/ggsmoothfit)



--

### ggplot2's geom_smooth() shows prediction across a range of values. 
--

### stat_smooth()'s xseq specifies positions at which to make predict.  
--

### {ggsmoothfit} piggybacks on StatSmooth, to easily draw fitted values, residuals, and more. 

<br><br><br><br><br>
<br>

--

| Gina Reynolds | 2023-10-25 |Image credit: Elena Koycheva, Upsplash


---


```{r}
library(tidyverse)
mtcars %>% 
  ggplot() + 
  aes(wt, mpg) +
  geom_point() +
  geom_smooth(se = F, method = lm) ->
a_ggplot2_plot
```



---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
a_ggplot2_plot +
  ggsmoothfit:::geom_fit(method = lm) + 
  ggsmoothfit:::geom_residuals(method = lm) 
```

---


`r flipbookr::chunk_reveal("feature2", widths = c(1,1))`

---

```{r feature2, echo = F, out.width="70%", fig.align='center', include = F}
a_ggplot2_plot + 
  ggsmoothfit:::geom_smooth_predict(
    xseq = 0, method = lm, size = 5) +
  ggsmoothfit:::geom_smooth_predict(
    xseq = 2, method = lm, size = 5) + 
  ggsmoothfit:::geom_smooth_predict(
    xseq = 3, method = lm, size = 5) +
  ggsmoothfit:::geom_smooth_step(
    xseq = 2:3, method = lm)
```


---

### Contribute

- https://github.com/EvaMaeRey/ggsmoothfit

---



### Check out stat_smooth() which does the computation in ggsmoothfit

- https://ggplot2.tidyverse.org/reference/geom_smooth.html
- examples with xseq, https://evamaerey.github.io/featurette/2023-10-30-stat-smooth-mtcars/stat-smooth-mtcars.html#10
- xseq documentation discussion https://github.com/tidyverse/ggplot2/issues/5246

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

