---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1629228136815-0fedb1808520?q=80&w=1632&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Nine pies, Dec 5th ... ]
## .small[featuring [{ggwedge}](https://github.com/everyday-analytics/ggwedge)]
#### .tiny[Gina Reynolds |Image credit: Kelcie Herald, Upsplash]
???
Title 

---


```{r}
library(tidyverse)

Titanic %>% 
  data.frame() %>% 
  uncount(weights = Freq) ->
titanic
```

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
titanic %>% 
  ggplot() + 
  ggwedge:::geom_pie() + 
  coord_polar() + # pie1
  aes(fill = Survived) + # pie2
  scale_fill_manual(
    values = c("darkgrey", 
               "cadetblue")) + # custom colors
  theme_void() + # little clean up
  ggwedge:::geom_pie_label(r_prop = 1.1) + #pie3
  facet_wrap(facets = vars(Sex)) + #pie4
  aes(r = 1) + #pie5
  aes(r0 = .6) + #pie6
  facet_grid(rows = vars(Sex), 
             cols = vars(Class)) + #pie7
  aes(label = after_stat(count)) + #pie8  
  aes(alpha = Age) + 
  scale_alpha_discrete(range = c(.6,1)) + #pie9
  # bonuspie back to percentages
  aes(label = after_stat(percent)) 
```




---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 90%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

