---
title: "#'Global Human Day' featurette"
subtitle: "featuring [{ggcirclepack}](https://github.com/EvaMaeRey/ggcirclepack) which is experimental"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, out.width = "80%")
# remotes::install_github("EvaMaeRey/ggcirclepack")
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1601312378427-822b2b41da35?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[#'tswift keys' featurette]
## .small[featuring [{ggbarlabs}](https://github.com/everyday_analytics/ggbarlabs) which is experimental]
#### .tiny[Gina Reynolds | 2023-10-26 |Image credit: David Pisnoy, Upsplash]
???
Title 

---


# What keys does Taylor Swift write in the most?

---

--

**key**: The estimated overall key of the track. Integers map to pitches using standard Pitch Class notation . E.g. 0 = C, 1 = C♯/D♭, 2 = D, and so on. If no key was detected, the value is -1.


---

```{r}
library(tidyverse)
taylor_album_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-17/taylor_album_songs.csv')
```

---
class: inverse, middle, center

# featured: ggbarlabs:::geom_barlab_count_percent


---

`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="80%", fig.align='center', fig.height=5, fig.width=8}
taylor_album_songs %>% 
  mutate(key_name = ifelse(mode, key_name, tolower(key_name))) %>% 
  filter(!is.na(key_mode)) %>% 
  ggplot() + 
  aes(x = fct_infreq(key_name)) + 
  geom_bar(alpha = .8) + 
  aes(fill = ifelse(mode, "major", "minor")) +
  scale_fill_manual(values = c("midnightblue", "magenta")) + 
  ggbarlabs::geom_barlab_count_percent(size = 3) +
  labs(title = "What Keys are Taylor Swift's Songs in?",
       caption = "In #tidytuesday's 2023-10-17/taylor_album_songs.csv",
       subtitle = "Number of Songs in keys from album songs by key") +
  ggbarlabs::defaults_ggbarlabs() + 
  labs(x = NULL) + 
  labs(fill = NULL)
```




---

### Contribute

- https://github.com/everyday-analytics/ggbarlabs



---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion:  https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette

