---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{}]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Denise Jans, Upsplash]
???
Title 

---

```{r}
library(tidyverse)
library(ggcirclepack)

# tidytuesday data
rladies_chapters_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-21/rladies_chapters.csv') %>% 
  mutate(chapter = str_remove(chapter, "rladies-") %>% 
           str_replace_all("-", " ") %>% str_to_title() %>% str_remove("\\s+$")) 
```




---

`r flipbookr::chunk_reveal("feature", widths = c(1,1))`



```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
rladies_chapters_raw %>% 
  ggplot() + 
  aes(x = "all", y = "all") + 
  stat_bin_2d(alpha = .85) +
  stat_bin_2d(geom = "text", 
           aes(label = after_stat(count)), 
           color = "oldlace",
           size = 3) +
  aes(y = wday(date, label = T, 
               week_start = "Monday") |> fct_rev()) + 
  scale_fill_viridis_c(option = "magma", end = .75) +
  aes(y = year(date) |> as.character() |> fct_rev()) + 
  aes(y = month(date, label = T)|> fct_rev()) +
  aes(x = year(date) |> as.character()) +
  aes(x = as.factor(day(date))) 
```

---

```{r, fig.width=15, fig.height=3}
ggwipe::last_plot_wipe_last() + # remove text layer, experimental
  facet_wrap(~year(date), nrow = 1) + 
  scale_x_discrete(breaks = as.character(1:31), # clean up x axis
                   labels = c("1", rep("", 8), 
                              "10", rep("", 9),
                              "20", rep("", 10), "31")) + 
  labs(x = "Day of Month") + 
  theme(panel.background = element_rect(fill = "darkgrey"),
        panel.grid = element_blank()) + 
  guides(fill = "colorbar")
```



```{r}



```


---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

