---
title: "prop is hard to use"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# [prop is hard to use](https://github.com/tidyverse/ggplot2/issues/5505)]
## .small[featuring [ggplot2/issues/5505]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Denise Jans, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
to_percent = function(x){(100*x) %>% round(1) %>% paste("%")}

library(tidyverse)
theme_set(theme_bw(base_size = 20))
Titanic %>% 
  data.frame() %>% 
  ggplot(aes(x = Sex, fill = Survived, weight = Freq)) +
  geom_bar(position = "dodge") +
  # Proportion per group
  aes(y     = after_stat(prop), group = Survived) +
  aes(label = to_percent(after_stat(prop))) + 
  stat_count(geom = "text", size = 4,
             position = 
               position_dodge2(width = .9, preserve = "single")) +
  scale_y_continuous(labels = scales::percent_format()) +
  # Proportion of total
  aes(y = after_stat(count / sum(count))) +
  aes(label = to_percent(after_stat(count / sum(count)))) +
  # Proportion per x position
  aes(y = after_stat(count / ave(count, x, FUN = sum))) +
  aes(label = to_percent(after_stat(count / ave(count, x, FUN = sum)))) +
  facet_wrap(~ Class) +
  # Proportion per panel
  aes(y = after_stat(count / ave(count, PANEL, FUN = sum))) +
  aes(label = to_percent(after_stat(count / ave(count, PANEL, FUN = sum)))) +
  # Proportion per panel and x position
  aes(y = after_stat(count / ave(count, x, PANEL, FUN = sum))) +
  aes(label = to_percent(after_stat(count / ave(count, x, PANEL, FUN = sum)))) +
  # Proportion per panel and fill
  aes(y = after_stat(count / ave(count, fill, PANEL, FUN = sum))) +
  aes(label = to_percent(after_stat(count / ave(count, fill, PANEL, FUN = sum))))
```


```{r}
layer_all_stages <- function(){

a <- ggtrace::layer_before_stat() %>% head(3)
b <- ggtrace::layer_after_stat() %>% head(3)
c <- ggtrace::layer_before_geom() %>% head(3)
d <- ggtrace::layer_after_scale() %>% head(3)

list(before_stat = a, after_stat = b, 
     before_geom = c, after_scale = d)

}



layer_all_stages()

```

---


```{r}
prop_by <- function(...) {
  count <- evalq(count, parent.frame())
  if (length(list(...)) == 0) {
    count / sum(count)
  } else {
    count / ave(count, ..., FUN = function(x) sum(abs(x)))
  }
}

ggplot(diamonds, aes(cut, fill = color)) +
  geom_bar(position = "dodge") + 
  aes(y = after_stat(prop_by()))

```



---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 85%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

