---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, cache = T)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1621634890180-0b93f32e10bb?q=80&w=1480&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Pie Charts w/ experimental ggwedge]
## .small[featuring [{ggwedge}] (https://github.com/everyday-analytics/ggwedge)]
#### .small[Gina Reynolds | 2023-11-28 |Image credit: Kelly Visel, Upsplash]
???
Title 

---

ggwedge::geom_pie() sell points


- dynamic pie chart creation (counts rows of data (w/ optional weight))
- area of chart is meaningful.  Defaults to 
- required aesthetics make sense (you don't need a "x" or "y" aesthetic, just fill (or alpha, or whatever))
- xy directions don't need to be coordinated (either geom_bar() or coord_polar defaults need to be adjusted to get a pie), since geom_pie anticipates that you'll use the geom w/ polar coordinates.
- labeling is relatively easy; positioning can be adjusted with r_prop (recommended) or r_nudge



---


`r flipbookr::chunk_reveal("test", widths = c(1,1), title = "### Example 1: ggplot2 calcs under the hood")`


```{r test, include = F}
library(tidyverse)
library(ggwedge)
ggplot2::diamonds %>% 
  ggplot() + 
  ggwedge:::geom_pie() + 
  coord_polar() +
  theme_void() +
  aes(fill = color) + 
  ggwedge:::geom_pie_label(r_prop = 1.2) +
  facet_wrap(~cut) +
  aes(alpha = color) +
  aes(alpha = NULL) + 
  aes(r = 1) + 
  facet_null() + 
  ggwedge:::geom_pie_label(
    aes(label = after_stat(weight), 
        angle = after_stat(c(0,0,0,0,0,0,-85)),
        color = after_scale(c(rep("white",6),"black"))),
    r_prop = .7)
```

---

# DIY aggregation: aggregate before entering plot space


---

`r flipbookr::chunk_reveal("count_yourself", widths = c(1,1),  title = "### Example 2: do your own aggregations")`


```{r count_yourself, include=F}
ggplot2::diamonds %>% 
  count(cut) %>% 
  ggplot() + 
  aes(fill = cut, weight = n) + 
  ggwedge:::geom_pie() +
  coord_polar() + 
  ggwedge:::geom_pie_label(
    aes(label = after_stat(weight), 
        angle = after_stat(c(85,0,0,0,0))),
    r_prop = .7, 
    color = "oldlace")
```


---

# to do...

- look at coord_radial and that interaction
- make geom_wedge which is cartesian coordinates (naive (?) crossing approach that works in 'step 0' base ggplot2 build, fails in stat creation.)
- make geom_pie_label variants helpers...; where stat calculates label based on some specification geom_pie_label(type = c("count", "percent", "count (percent)", "percent (count)", "fill", etc)...


---

## 'Real world' application: TidyTuesday Rladies

```{r, fig.height=6, fig.width=10}
# tidytuesday data
rladies_chapters <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-21/rladies_chapters.csv')
```


---


`r flipbookr::chunk_reveal("feature", widths = c(1,1), title = "## Make pies for RLadies attendance")`



```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)
library(ggwedge)
rladies_chapters  %>% 
  filter(year == 2020) %>% 
  ggplot() + 
  ggwedge:::geom_pie(color = "snow", 
                     linewidth = .25) + 
  aes(fill = location) + 
  coord_polar(clip = "on") +
  theme(axis.text.x = element_blank()) +
  ggwedge:::geom_pie_label(r_prop = 1.2, 
                           color = "gray20",
                           size = 2) +
  facet_wrap(~month(date, label = T, abbr = T), 
             nrow = 3) + 
  scale_fill_manual(values = c("Plum3", "Magenta")) ->
a_nice_plot
```

---


`r flipbookr::chunk_reveal("style", widths = c(1,1), title = "## Style plot")`

---

```{r style, echo = F}
a_nice_plot +   
  theme(plot.title.position = "plot") + 
  labs(title = "R-Ladies meetings in 2020 moved from mostly <span style = 'color:Plum3;'>in person</span> to mostly <span style = 'color:Magenta;'>online</span>.") +
  labs(subtitle = "There was also a drop in the number of April/May meetings.\n") +
  theme_void() +
  theme(
    plot.title = ggtext::element_textbox_simple(
      size = 14, lineheight = 1, padding = margin(0, 0, 5, 0)
    )
  ) + 
  theme(text = element_text(color = "grey55")) + 
  theme(legend.position = "none")
```




---

### Contribute

- https://github.com/everyday-analytics/ggwedge

---



### There are many other approaches to pies.  

- base ggplot2: https://r-graph-gallery.com/piechart-ggplot2.html, aan be used on aggregates or raw data (stat_count is at work in the background)

- ggforce https://ggforce.data-imaginist.com/reference/geom_arc_bar.html cartesian coords, highly flexible, requires many aesthetics, no auto label, requires pre-aggregation
- ggpie #1 https://github.com/showteeth/ggpie  wrapping style ggplot2 extension ggpie (data, group_key, count_type, fill_color)
- ggpie #2 https://github.com/Rkabacoff/ggpie wrapping style
- ggpie #3 https://github.com/marcuslehr/ggpie not a package, just a little script in a repo on github
- ggtricks https://github.com/AbdoulMa/ggtricks geom_pie cartesian, requires pre-aggregation

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

