---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1621634890180-0b93f32e10bb?q=80&w=1480&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Pie Charts w/ experimental ggwedge]
## .small[featuring [{ggwedge}](https://github.com/everyday-analytics/ggwedge) ...]
#### .small[Gina Reynolds | 2023-11-28 |Image credit: Kelly Visel, Upsplash]
???
Title 

---

## Data

```{r}
# tidytuesday data
rladies_chapters <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-21/rladies_chapters.csv')
```


---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)
library(ggwedge)
rladies_chapters  %>% 
  filter(year == 2020) %>% 
  ggplot() + 
  aes(fill = location) + 
  ggwedge:::geom_pie(color = "snow", linewidth = .25) + 
  ggwedge:::geom_pie_label(r_prop = 1.2, 
                           color = "gray20",
                           size = 2) +
  coord_polar() +
  facet_wrap(~month(date, label = T, abbr = T), 
             nrow = 2) + 
  theme(legend.position = "none",
        legend.justification = 0) +
  aes(r = 1) + 
  aes(r = NULL) + 
  scale_fill_manual(values = c("Plum3", "Magenta")) +
  labs(title = "RLadies moved from in person to mostly online in 2020") +
  theme(plot.title.position = "plot") + 
  labs(title = "R-Ladies meetings in 2020 moved from mostly <span style = 'color:Plum3;'>in person</span> to mostly <span style = 'color:Magenta;'>online</span>.") +
  labs(subtitle = "There was also a drop in the number of April/May meetings.\n") +
  theme_void() +
  theme(
    plot.title = ggtext::element_textbox_simple(
      size = 14, lineheight = 1, padding = margin(0, 0, 5, 0)
    )
  ) + 
  theme(text = element_text(color = "grey55")) + 
  theme(legend.position = "none")
```


---

### Contribute

- https://github.com/everyday-analytics/ggwedge

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

