---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1669147849966-534dc594fc85?q=80&w=1470&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{ggnaturalearth}](https://github.com/EvaMaeRey/ggnaturalearth) - which exists to test and refine ggnorthcarolina, a template repo, and which makes some promising choropleths!]
#### .tiny[Gina Reynolds | 2023-12-18 |Image credit: Denise Jans, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)
library(ggnaturalearth)
options(scipen = 10)
gapminder::gapminder |>
  filter(year == 2002) %>% 
  ggplot() +
  aes(country_name = country) +
  geom_country() + 
  aes(fill = pop/1000000) + 
  labs(fill = "Pop (millions)") +
  scale_fill_viridis_c(trans = "log10") +
  aes(label = country) +
  geom_country_label(size = 1.5,
                     check_overlap = T) + 
  geom_country(keep_country = 
                 c("Portugal", "Germany"), 
               color = "darkred", 
               linewidth = .5,
               alpha = 0) +
  coord_sf(xlim = c(-25, 35), ylim = c(30, 80)) + 
  ggstamp::theme_void_fill("aliceblue")
```


---

### Contribute

- https://github.com/EvaMaeRey/ggnorthcarolina

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

