---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{}]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Denise Jans, Upsplash]
???
Title 




---
class: inverse, center, middle

# And a little ggpie preview... (this will probably move to to it's own)

```{r}
library(tidyverse)
Titanic %>% 
  data.frame() %>% 
  uncount(Freq) ->
tidytitanic

```

---


`r flipbookr::chunk_reveal("feature2", widths = c(1,1))`


```{r feature2, echo = F, out.width="70%", fig.align='center', include = F}
library(ggpie)
tidytitanic %>%
  ggpie() + 
   geom_wedge() + 
   aes(fill = Sex) + 
  facet_wrap(~ Sex) + 
  aes(fill = Class) + 
  facet_grid(Sex ~ Class) + 
  aes(fill = Survived)
```


---

### Contribute

- https://github.com/EvaMaeRey/ggpie (may become ggwedge)


---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette



