---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1561336313-0bd5e0b27ec8?q=80&w=1470&auto=format&fit=crop&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# Dec 6th]
## .small[A [{ggsample}](https://github.com/EvaMaeRey/ggsample) feature]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: René Porter, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1.2,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
library(ggsample)

mtcars %>% 
  ggplot() + 
  aes(x = wt, y = mpg) + 
  geom_point(alpha = .5) + 
  theme_gray(base_size = 18) +
  geom_smooth(method = lm, se = F) + 
  ggxmean::geom_lm_formula(size = 8) + 
  coord_cartesian(xlim = c(1,6), 
                  ylim = c(5,35))
```



---

## Demoing: 

- ### facet_sample(n_sampled = 15, n_facets = 4) 

--

- ### facet_sample_prop(n_facets = 9, prop = .3) 

--

- ### facet_scramble(n_facets = 4)

--

- ### facet_bootstrap(n_facets = 9) + geom_count() 

--

- ### facet_bootstrap(n_facets = **1**) + geom_count() 
--
*look at individual samples*

--

### Background... mostly borrowing from The facet_* functions mostly borrow from the ggplot2 extension vignette [(extending existing facet function)](https://github.com/tidyverse/ggplot2/blob/5f518d02af27160ab98fed736a472321d72d10d2/vignettes/extending-ggplot2.Rmd#L1028)


---


`r flipbookr::chunk_reveal("feature1", widths = c(1.3,1), break_type = "rotate")`

```{r feature1, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
library(ggsample)

mtcars %>% 
  ggplot() + 
  aes(x = wt, y = mpg) + 
  geom_point(alpha = .5) + 
  theme_gray(base_size = 20) +
  geom_smooth(method = lm, se = F) +
  ggxmean::geom_lm_formula(size = 5) +
  coord_cartesian(xlim = c(1,6), 
                  ylim = c(5,35)) +
  facet_sample(n_sampled = 15, n_facets = 4) + #ROTATE
  facet_sample_prop(n_facets = 9, prop = .3) + #ROTATE
  facet_scramble(n_facets = 4) + #ROTATE
  facet_bootstrap(n_facets = 9) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() + #ROTATE
  facet_bootstrap(n_facets = 1) + geom_count() #ROTATE
```



---

### Contribute

- https://github.com/EvaMaeRey/ggsample


---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 130%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

