---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{}]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Denise Jans, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)
major = c("C", "G", "D", "A", "E", "B",
            "F#/Gb","C#/Db", "G#/Ab", "Eb", "Bb", "F")
minor = c("Am", "Em", "Bm", "F#m", "C#m", "G#m", "Ebm",
            "Bbm", "Fm", "Cm", "Gm", "Dm")

major_roman = c("I", "V", "II", "VI", "III", "VII", rep("",5), "IV")

major %>% 
  tibble(minor) %>% 
  ggplot() + 
  aes(fill = major) + 
  ggwedge:::geom_pie(show.legend = F, 
                     color = "black", 
                     alpha = .4,
                     linewidth = .1) +
  aes(r = 1) +
  coord_polar(start = -pi/12) +
  ggwedge:::geom_pie_label(aes(label = after_stat(major)),
                 r_prop = .85, size = 6) +
  aes(angle = after_stat(angle_wedge -90+180/12)) + 
  ggwedge:::geom_pie_label(aes(label = after_stat(minor)),
                 r_prop = .5, size = 4.5) +
  theme_void() +
  geom_hline(yintercept = 1.2, alpha = 0) 
```





---


`r flipbookr::chunk_reveal("feature2", widths = c(1,1))`

```{r feature2, include = F}
last_plot() + 
  ggwedge:::geom_pie_label(show.legend = F, 
           color = "black", r_prop = 1.1,
           aes(label = after_stat(major_roman)),
           linewidth = .1) + 
  ggwedge:::geom_pie(alpha = 0, color = "grey",  
                     aes(r0 = 1, r = 1.2, 
                         lty = after_stat(ifelse(major_roman == "I", "a", 
                                                       ifelse(major_roman %in% c("V", "IV"), "b", 
                                                              ifelse(major %in% c("Bb", "D"), "c", "d")))))
                     ) +
  theme(legend.position = "none") ->
p
```




---


### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

