---
title: "#'stat_smooth' featurette"
subtitle: "featuring [{ggcirclepack}](https://github.com/EvaMaeRey/ggcirclepack) which is experimental"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
# remotes::install_github("EvaMaeRey/ggcirclepack")
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1492144534655-ae79c964c9d7?auto=format&fit=crop&q=80&w=1583&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[#'ggplot::stat_smooth' featurette]
## .small[featuring [ggplot2::stat_smooth() ](https://github.com/tidyverse/ggplot2/) and mtcars]
#### .tiny[Gina Reynolds | 2023-10-25 |Image credit: Peter Broomfield, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
library(tidyverse)
mtcars %>% 
  ggplot(aes(wt, mpg)) +
  geom_point() +
  geom_smooth() + 
  stat_smooth(geom = "point", 
              color = "blue", 
              xseq = mtcars$wt) +
  stat_smooth(geom = "segment",  
              color = "darkred",   
              xseq = mtcars$wt,
              xend = mtcars$wt,
              yend = mtcars$mpg) + 
  # intercept for linear model
  stat_smooth(geom = "point",
             color = "green",
             xseq = 0,
             method = lm,
             size = 7) + 
  stat_smooth(color = "green",
              xseq = c(0, mtcars$wt),
              method = lm)
```




---



### Check out {ggplot2} which does the computation in ggcirclepack

- https://github.com/tidyverse/ggplot2/


---

### Check out {ggsmoothfit} which explores more stat_smooth uses for educators

- https://github.com/EvaMaeRey/ggsmoothfit

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette

