---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
# remotes::install_github("EvaMaeRey/ggcirclepack")
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1502740479091-635887520276?auto=format&fit=crop&q=80&w=1469&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# A featurette: How do you retrieve R help file as text?]
## .small[Featuring baptnz@vis.social's R help retrieval]
#### .tiny[Gina Reynolds | 2023-11-02 |Image credit: Zhen H, Upsplash]
???
Title 

---


`r flipbookr::chunk_reveal("feature", widths = c(1,1))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(magrittr)

tmp <- tempfile()

help(mtcars, package = datasets) %>% 
  as.character() %>% 
  utils:::.getHelpFile() %>% 
  tools:::Rd2latex(Rd = ., out = tmp)

pandoc::pandoc_convert(file = tmp, 
                       from = "latex", 
                       to = 'markdown') ->
  md
```

---

Also: possible alternative route https://yihui.org/rd2roxygen/

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette

