---
title: "featurette"
subtitle: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(tidyverse.quiet = TRUE)
```

class: inverse, left, bottom
background-image: url(https://images.unsplash.com/photo-1542204165-65bf26472b9b?auto=format&fit=crop&q=80&w=1548&ixlib=rb-4.0.3&ixid=M3wxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8fA%3D%3D)
background-size: cover
# .Large[# My featurette]
## .small[featuring [{}]() ...]
#### .tiny[Gina Reynolds | 2023-10-25 | Image credit: Denise Jans, Upsplash]
???
Title 

---




`r flipbookr::chunk_reveal("feature", break_type = "replace", widths = c(1,2), replace = "range", replacements = c("is_free", "range" ,  "setup_panel_params" , "render_axis_v"  ,     "backtransform_range", "transform"         ,  "distance"       ,     "render_bg"   , "render_axis_h"     , "super"          ,     "is_linear"))`

---

```{r feature, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
ggplot2::CoordCartesian %>% 
  .$range
```

---


`r flipbookr::chunk_reveal("feature2", break_type = "replace", widths = c(1,2), replace = "range", replacements = names(ggplot2::CoordRadial))`

---

```{r feature2, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
ggplot2::CoordRadial %>% 
  .$range
```



---


`r flipbookr::chunk_reveal("feature3", break_type = "replace", widths = c(1,2), replace = "aesthetics", replacements = names(ggplot2::StatCount))`

---

```{r feature3, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
ggplot2::StatCount %>% 
  .$aesthetics
```



`r flipbookr::chunk_reveal("feature4", break_type = "replace", widths = c(1,2), replace = "aesthetics", replacements = names(ggplot2::GeomBar))`

---

```{r feature4, echo = F, out.width="70%", fig.align='center', include = F}
# tidytuesday data
library(tidyverse)
ggplot2::GeomBar %>% 
  .$aesthetics
```


---

### Contribute

- https://github.com/EvaMaeRey/ggcirclepack

---



### Check out {packcircles} which does the computation in ggcirclepack

- https://github.com/mbedward/packcircles

---

### Check out flipbookr, used to build this featurette

- https://github.com/EvaMaeRey/flipbookr
- discussion: https://github.com/EvaMaeRey/flipbookr/blob/master/docs/draft_jasa_submission.pdf 

---

### Check out more featurettes

- https://EvaMaeRey.github.io/featurette




```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 100%}
@media print {
  .has-continuation {
    display: block;
  }
}
```

